---
title: "uncertainty_comms"
author: "Doug McNeall"
date: "30 November 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Analysing the results of the Winton Centre Uncertainty Communication Workshop
# 26-27 November 2018


```{r preamble, echo=FALSE, include=FALSE}
library(RColorBrewer)
library(viridisLite)
library(fields)

br = rev(brewer.pal(11, 'RdBu'))
byr = rev(brewer.pal(11, 'RdYlBu'))
blues = rev(brewer.pal(9, 'Blues'))

dat = read.csv("data/M2D+Workshop+questionnaire_msedit.csv")

belief = dat[,'Do.you.believe.global.warming.is.caused.by.human.activities']
worried = dat[,'How.worried.are.you.about.global.warming']
domore = dat[,'Do.you.think.people.should.do.more.']
dempol = dat[,'DemPol']
occur = dat[,'occur']
unc1 = dat[,'unc1_1']

```

## How does belief in global warming interact with other aspects?

Respondants were asked "Do you believe global warming is caused by human activities?" before the survey, along with some other questions.

### How worried are you about global warming?
```{r belief_v_worried, echo=FALSE}
#png('graphics/belief_v_worried.png')
par(mfrow = c(1,2), mar = c(5,5,1,1), las = 1, pty = 's')
plot(jitter(belief), jitter(worried), cex = 0.6,
     xlab = '', ylab = ''
)
mtext('Do you believe global warming\n is caused by human activities?', side = 1,outer = TRUE, line = -3)
title(ylab = 'How worried are you\n about global warming?', line = 3)
#dev.off()

belief.worried.tab = table(belief, worried)

par(mar = c(5,1,1,5))
image.plot(x = 1:7, y = 1:7, z = belief.worried.tab, col = byr,
           xlab = '', ylab = '')

print(belief.worried.tab)
```



### Do you think people should be doing more or less to reduce global warming?

```{r belief_v_domore, echo=FALSE}
#png('graphics/belief_vs_domore.png')
par(mfrow = c(1,2), mar = c(5,5,1,1), las = 1, pty = 's')
plot(jitter(belief), jitter(domore), cex = 0.6,
     xlab = '', ylab = ''
)
mtext('Do you believe global warming\n is caused by human activities?', side = 1,outer = TRUE, line = -3)
title(ylab = 'Do you think people should be doing\n more or less to reduce global warming?', line = 3)
#dev.off()

belief.domore.tab = table(belief, domore)

par(mar = c(5,1,1,5))
image.plot(x = 1:7, y = 1:7, z = belief.domore.tab, col = byr,
           xlab = '', ylab = '')

print(belief.domore.tab)

```

### Political leaning - Liberal to Conservative

```{r belief_v_dempol, echo=FALSE}
#png('graphics/belief_vs_dempol.png')
par(mfrow = c(1,2), mar = c(5,5,1,1), las = 1, pty = 's')
plot(jitter(belief), jitter(dempol), cex = 0.6,
     xlab = '', ylab = ''
)
mtext('Do you believe global warming\n is caused by human activities?', side = 1,outer = TRUE, line = -3)
title(ylab = 'Liberal to Conservative', line = 3)
#dev.off()

belief.dempol.tab = table(belief, dempol)

par(mar = c(5,1,1,5))
image.plot(x = 1:7, y = 1:7, z = belief.dempol.tab, col = byr,
           xlab = '', ylab = '')
print(belief.dempol.tab)
```
### Given the information you've just seen ... how likely do you think it is that this event will occur?
```{r belief_v_occur, echo=FALSE}
#png('graphics/belief_vs_occur.png')
par(mfrow = c(1,2), mar = c(5,5,1,1), las = 1, pty = 's')
plot(jitter(belief), jitter(occur), cex = 0.6,
     xlab = '', ylab = ''
)
mtext('Do you believe global warming\n is caused by human activities?', side = 1,outer = TRUE, line = -3)
title(ylab = '... how likely do you think it is\n that this event will occur', line = 3)

belief.occur.tab = table(belief, occur)

par(mar = c(5,1,1,5))
image.plot(x = 1:7, y = 1:7, z = belief.occur.tab, col = byr,
           xlab = '', ylab = '')

print(belief.occur.tab)
```

```{r dempol_v_uncertainty, echo=FALSE}

#png('graphics/belief_vs_occur.png')
par(mfrow = c(1,2), mar = c(5,5,1,1), las = 1, pty = 's')
plot(jitter(dempol), jitter(unc1), cex = 0.6,
     xlab = '', ylab = ''
)
mtext('Liberal to Conservative', side = 1,outer = TRUE, line = -3)
title(ylab = 'How much uncertainty is there about this information', line = 3)

dempol.unc1.tab = table(dempol, unc1)

par(mar = c(5,1,1,5))
image.plot(x = 1:7, y = 1:10, z = dempol.unc1.tab, col = byr,
           xlab = '', ylab = '')

print(dempol.unc1.tab)
```
